Eco-evolutionary dynamics of finite populations from first principles

### 2023-04-08 ind_files/99_Appendix_D_examples.tex
Link to GitHub repo for scripts (to be made public later)

>>>>

This appendix provides several examples of the birth-death processes studied in this thesis. The material covered in this thesis, including the examples in this Appendix, are currently being written up for publication. Consequently, the GitHub repository containing the scripts used to make the plots presented below is currently private. The repository will be made public after publication, and you should be able to access it via \href{https://github.com/ThePandalorian/Bhat_MS_thesis_scripts}{this link} (which will not work until I make the repository public) if you are reading this after the material is published; Until then, scripts are available on request, just drop me an email.
